TO FIND

### 2013-05-16 ms.tex
Minor edits in the last paragraphs

We will adopt the perspective that neutral theory is a useful tool to both
understand and predict the impact of dispersal on community organization. Even
for a theoretical analysis, we need a benchmark without niche differences to
reveal the role of dispersal in structuring communities and understand the
interaction with niche differentiation. We will explore recent applications of
neutral theory, at the crossroad of network theory, to better represent the
impact of landscape structure on biodiversitity distribution. This analysis will
prove particularly relevant to limnology, where most riverine and lacustre
habitats are characterized by a their discrete nature and spatially complex
arrangements. We will also reveal the relative contribution of ecological
interaction and niche differentiation by contrasting predictions of a neutral
model to other metacommunity perspectives.

>>>>

In this paper, we argue that neutral theory is useful both to understand and
predict the impact of dispersal on community organization. Even
for purely theoretical analyses, we need a benchmark without niche differences to
reveal the role of dispersal in structuring communities, and understand how it
interacts with niche differentiation. We will explore recent applications of
neutral theory, at the crossroad of network theory, to better represent the
impact of landscape structure on biodiversitity distribution. This analysis will
prove particularly relevant to limnology, where most riverine and lacustre
habitats are characterized by a their discrete nature and spatially complex
arrangements. We will also reveal the relative contribution of ecological
interaction and niche differentiation by contrasting predictions of a neutral
model to other metacommunity perspectives.
